MSnbase, efficient and elegant R-based processing and visualisation of raw mass spectrometry data

### 2020-09-07 large_experiment_processing.Rmd
Update Rmd

---
title: "Supplementary data for: \\textit{`MSnbase`, efficient and elegant R-based processing and visualisation of raw mass spectrometry data}"
author: "Laurent Gatto, Sebastian Gibb and Johannes Rainer"
output:
    BiocStyle::pdf_document:
        includes:
            in_header: "header.sty"
---

>>>>

---
title: "MSnbase, efficient and elegant R-based processing and visualisation of raw mass spectrometry data"
author:
  - name: Laurent Gatto
    affiliation: Computational Biology Unit, de Duve Institute, Universit\'e catholique de Louvain, Brussels, Belgium
  - name: Sebastian Gibb
    affiliation: Department of Anaesthesiology and Intensive Care of the University Medicine Greifswald, Germany
  - name: Johannes Rainer
    affiliation: Institute for Biomedicine, Eurac Research, Affiliated Institueof the University of L\"ubeck, Bolzano, Italy
output: 
  rticles::acs_article:
---
